Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-07 General WLD combinatorics.tex
Inside/outside dfn version 2.2.1

This in turn defines two sets of propagators, $\{\cP_{in}, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas The set $\cP_{in}$ (resp. $\cP_{out}$) is the set of propagators, not equal to $p$ \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp. $V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are both on the inside and outside of $p$. Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$. Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side. In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.

>>>>

This in turn defines two sets of propagators, $\{\cP_{in}, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas The set $\cP_{in}$ (resp. $\cP_{out}$) is the set of propagators, not equal to $p$ \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp. $V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are neither on the inside and outside of $p$. Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$. Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side. In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
